### 2021-06-22 src/paper/report.tex
Temp.

    \floatfoot{\noindent \textit{Note:} A        % formal
        description of the model can be found in Supplementary Material~\ref{sec:model}.
        Figure~\ref{fig:model_contacts_infections} shows the influence on an agent's
        contacts to other agents. Demographic characteristics set the baseline number of
        contacts in different networks. She may reduce the number of contacts due to
        NPIs, showing symptoms, or testing positively for SARS-CoV-2. Infections may
        occur when a susceptible agent meets an infectious agent; the probability depends
        on the type of contact, on seasonality, and on NPIs. If infected, the infection
        progresses as depicted in Figure~\ref{fig:model_disease_progression}. If rapid
        tests are available, agents' demand is modeled as in
        Figure~\ref{fig:model_rapid_tests}. \textcolor{blue}{For each reason only a share
        of eligible individuals receive a test. The share of eligible individuals that
        get tested depends on the reason and changes over time (see
        Figure~\ref{fig:rapid_test_demand}).} \textcolor{red}{All pupils are attending
        school are tested, other reasons trigger a test only for a fraction of
        individuals.} Figure~\ref{fig:model_official_cases} shows the model of
        translating all infections in the simulated data to age-specific recorded
        infections. The model uses data on the aggregate share of recorded cases, on the
        share of positive PCR tests triggered by symptoms, \textcolor{red}{and on the
        false positive rate of rapid tests}. The lower part of the graph is relevant only
        for periods where rapid tests are available.}
\end{figure}

@@

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
some days to be processed and there are aggregate capacity constraints throughout. In
contrast, rapid antigen tests yield immediate results; after a phase-in period, all tests
that are demanded will be performed.\comment[id=K]{Might be problematic to talk about
supply and demand here. We don't have supply and demand (except for maybe employers and
employees) and I would not interpret the increases in April as an easing of supply side
constraints.} Specificity and sensitivity of these tests is set according to data
analyzed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the timing of the test
relative to the onset of infectiousness. Figure~\ref{fig:model_rapid_tests} shows our
model for rapid test demand. Schools may require staff and students to be tested
regularly. Rapid tests may be offered by employers to on-site workers. Individuals may
demand tests for private reasons, which include having plans to meet other people,
showing symptoms of CoViD-19, and because a household member tested positively for the
virus. We endow each agent with an individual compliance parameter. This parameter
determines whether she takes up rapid tests\deleted[id=K]{offered by employers or
follows up on private reasons} % compliance also determines who is tested in education settings
.\footnote{A positive test result (of either kind), as well as symptoms leads most
individuals to reduce their contacts; this is why tests impact the actual contacts in
Figure~\ref{fig:model_description}.}

%%% ===================================================================================

@@

The main issue with official case numbers is that they will contain only a fraction of
all infections. We thus model official cases as depicted in
Figure~\ref{fig:model_official_cases}.\comment[id=K]{I don't understand why we mention
the false positive rates in the floatfoot of this. I would either mention rapid test
sensitivity and specificity in general or not mention them at all.} We take aggregate
estimates of the share of detected cases and use data on whether CoViD-19 symptoms led to
a PCR test. As the share of asymptomatic individuals varies by age group, this gives us
age-specific shares (see Figure~\ref{fig:share_known_cases_by_age_group} for the share of
known cases by age group over time in our model). Our estimates suggest that---in the
absence of rapid testing---the detection rate is on average 80\% higher for individuals
above age 80 compared to school age children. Once rapid test become available,
confirmation of a positive result is another reason leading to positive PCR tests.

@@

The effects of various mechanisms can be disentangled due to the distinct temporal
variation in the drivers of the pandemic. Next to the stringency index, the three lines
in Figure~\ref{fig:stringency_infectious_contacts} summarize how contact reductions,
increased hygiene regulations, and seasonality evolved since early September for each of
the three broad contact networks. For example, a value of 0.75 for the work multiplier
means that if the environment was the same as in September (levels of infection rates,
no rapid tests or vaccinations, only the wildtype virus present), infections at the
workplace would be reduced by 25\%. The lines show the product of the effect of contact
reductions, increased hygiene regulations, and seasonality. Two aspects are particularly
interesting. First, all lines broadly follow the stringency index and they would do so
even more if we left out seasonality and school vacations (roughly the last two weeks of
October, two weeks each around Christmas and Easter, and some days in late May). Second,
the most stringent regulations are associated with the period of strong decreases in new
infections between late December 2020 and mid-February 2021. The reversal of the trend
is associated with the spread of the B.1.1.7 variant. The steep drop in recorded cases
during May 2021 is associated with at least weekly rapid tests to 42\% of the
population, a vaccination rate that rose from 28\% to 43\%, and mostly seasonality
impacting a fall in the relative infectiousness of contacts outside of work and school.

In order to better understand the contributions  of rapid tests, vaccinations, and
seasonality on the evolution of infections in 2021,
Figure~\ref{fig:2021_scenarios_broad} considers various scenarios. NPIs are always the
same as in the baseline scenario. Figure~\ref{fig:2021_scenarios_recorded} shows the
model fit (the blue line, same as in Figure~\ref{fig:aggregated_fit}), a scenario
without any of the three factors (red line), and three scenarios turning these factors
off one by one. Figure~\ref{fig:2021_scenarios_newly_infected} does the same for total
infections in the model. Figure~\ref{fig:2021_scenarios_decomposition} employs Shapley
values \citep{Shapley2016} to decompose the difference in total infections between the
scenario without any of the three factors and our main specification.

@@

Until mid-March, there is no visible difference between the different scenarios.
Seasonality hardly changes, and only few vaccinations or rapid tests were administered.
Even thereafter, the effect of the vaccination campaign is surprisingly small at first
sight. Whether considering recorded or total infections with only one channel active,
the final level is always the highest in case of the vaccination campaign (orange
lines). The Shapley value decomposition shows that vaccinations contribute 17\% to the
cumulative difference between scenarios. Reasons for this are the slow start---it took
until March~24th until 10\% of the population had received their first vaccination, the
20\% mark was reached on April 19th---and the focus on older individuals. These groups
contribute less to the spread of the disease than others due to a lower number of
contacts, see Supplementary Material~\ref{subsec:contacts_by_age}. By the end of our
study period, when first-dose vaccination rates reached around 40\% of the population,
the numbers of new cases would have started to decline. It is important to note that the
initial focus of the campaign was to prevent deaths and severe disease. Indeed, the case
fatality was rate considerably lower during the third wave when compared to the second
(4.4\% between October and February and 1.4\% between March and the end of May).

>>>>

    \floatfoot{\noindent \textit{Note:} A        % formal
        description of the model can be found in Supplementary Material~\ref{sec:model}.
        Figure~\ref{fig:model_contacts_infections} shows the influence on an agent's
        contacts to other agents. Demographic characteristics set the baseline number of
        contacts in different networks. She may reduce the number of contacts due to
        NPIs, showing symptoms, or testing positively for SARS-CoV-2. Infections may
        occur when a susceptible agent meets an infectious agent; the probability depends
        on the type of contact, on seasonality, and on NPIs. If infected, the infection
        progresses as depicted in Figure~\ref{fig:model_disease_progression}. If rapid
        tests are available, agents' demand is modeled as in
        Figure~\ref{fig:model_rapid_tests}. For each reason only a share of eligible
        individuals receive a test depending on an individual compliance parameter.
        Figure~\ref{fig:model_official_cases} shows the model of translating all
        infections in the simulated data to age-specific recorded infections. The model
        uses data on the aggregate share of recorded cases, on the share of positive PCR
        tests triggered by symptoms, and on the false positive rate of rapid tests. The
        lower part of the graph is relevant only for periods where rapid tests are
        available.}
\end{figure}

@@

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
some days to be processed and there are aggregate capacity constraints throughout. In
contrast, rapid antigen tests yield immediate results; after a phase-in period, all tests
that are demanded will be performed. Specificity and sensitivity of these tests is set
according to data analyzed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the
timing of the test relative to the onset of infectiousness.
Figure~\ref{fig:model_rapid_tests} shows our model for rapid test demand. Schools may
require staff and students to be tested regularly. Rapid tests may be offered by
employers to on-site workers. Individuals may demand tests for private reasons, which
include having plans to meet other people, showing symptoms of CoViD-19, and because a
household member tested positively for the virus. We endow each agent with an individual
compliance parameter. This parameter determines whether she takes up rapid
tests\deleted[id=K]{offered by employers or follows up on private reasons}% compliance also determines who is tested in education settings
.\footnote{A positive test result (of either kind), as well as symptoms leads most
individuals to reduce their contacts; this is why tests impact the actual contacts in
Figure~\ref{fig:model_description}.}

@@

The main issue with official case numbers is that they will contain only a fraction of
all infections. We thus model official cases as depicted in
Figure~\ref{fig:model_official_cases}. We take aggregate estimates of the share of
detected cases and use data on \replaced[id=K]{the share of PCR tests administered to
people with CoViD-19 symptoms}{whether CoViD-19 symptoms led to a PCR test}. As the share
of asymptomatic individuals varies by age group, this gives us age-specific shares (see
Figure~\ref{fig:share_known_cases_by_age_group} for the share of known cases by age group
over time in our model). Our estimates suggest that---in the absence of rapid
testing---the detection rate is on average 80\% higher for individuals above age 80
compared to school age children. Once rapid test become available, confirmation of a
positive result is another reason leading to positive PCR tests.

@@

The effects of various mechanisms can be disentangled due to the distinct temporal
variation in the drivers of the pandemic. Next to the stringency index, the three lines
in Figure~\ref{fig:stringency_infectious_contacts} summarize how contact reductions,
increased hygiene regulations, and seasonality evolved since early September for each of
the three broad contact networks. For example, a value of 0.75 for the work multiplier
means that if the environment was the same as in September (levels of infection rates, no
rapid tests or vaccinations, only the wildtype virus present), infections at the
workplace would be reduced by 25\%. The lines show the product of the effect of contact
reductions, increased hygiene regulations, and seasonality. Two aspects are particularly
interesting. First, all lines broadly follow the stringency index and they would do so
even more if we left out seasonality and school vacations (roughly the last two weeks of
October, two weeks each around Christmas and Easter, and some days in late May). Second,
the most stringent regulations are associated with the period of strong decreases in new
infections between late December 2020 and mid-February 2021. The reversal of the trend is
associated with the spread of the B.1.1.7 variant. The steep drop in recorded cases
during May 2021 is associated with at least weekly rapid tests for 42\% of the
population, a vaccination rate that rose from 28\% to 43\%, and \deleted[id=K]{mostly}
seasonality \replaced[id=K]{further lowering}{impacting a fall in} the relative
infectiousness of contacts \deleted[id=K]{outside of work and school.}

In order to better understand the contributions  of rapid tests, vaccinations, and
seasonality on the evolution of infections in 2021, Figure~\ref{fig:2021_scenarios_broad}
considers various scenarios. NPIs are always the same as in the baseline scenario.
Figure~\ref{fig:2021_scenarios_recorded} shows the model fit (the blue line, same as in
Figure~\ref{fig:aggregated_fit}), a scenario without any of the three factors (red line),
and three scenarios turning \replaced[id=K]{each factor on individually}{these factors
off one by one}. Figure~\ref{fig:2021_scenarios_newly_infected} does the same for total
infections in the model. Figure~\ref{fig:2021_scenarios_decomposition} employs Shapley
values \citep{Shapley2016} to decompose the difference in total infections between the
scenario without any of the three factors and our main specification.

@@

Until mid-March, there is no visible difference between the different scenarios.
Seasonality hardly changes, and only few vaccinations and rapid tests were administered.
Even thereafter, the effect of the vaccination campaign is surprisingly small at first
sight. Whether considering recorded or total infections with only one channel active,
the final level is always the highest in case of the vaccination campaign (orange
lines). The Shapley value decomposition shows that vaccinations contribute 17\% to the
cumulative difference between scenarios. Reasons for this are the slow start---it took
until March~24th until 10\% of the population had received their first vaccination, the
20\% mark was reached on April 19th---and the focus on older individuals. These groups
contribute less to the spread of the disease than others due to a lower number of
contacts\replaced[id=K]{as they do not work, do not go to school and tend to live in small households}{, see Supplementary Material~\ref{subsec:contacts_by_age}}.
% We don't draw age specific number of contacts because the sample sizes would be to
% small.
By the end of our study period, when first-dose vaccination rates reached around 40\% of
the population, the numbers of new cases would have started to decline. It is important
to note that the initial focus of the campaign was to prevent deaths and severe disease.
Indeed, the case fatality was rate considerably lower during the third wave when compared
to the second (4.4\% between October and February and 1.4\% between March and the end of
May).\comment[id=K]{This needs a source.}
